\documentclass[a4paper]{article}

\usepackage[voffset=0cm]{geometry}
\setlength{\parindent}{0cm}
\pagenumbering{gobble}

\input{000_metadata}

\begin{document}
\begin{tabular}{@{}p{0.25\textwidth}p{0.72\textwidth}@{}}
    PhD candidate’s name: & \theauthor{} \\
    First promotor: & \firstpromotor{} \\
    Title of PhD thesis: & \thetitle{} \\
    Date of public defence: & \defencedate{}
\end{tabular}

\paragraph{Chapter 1 General introduction.}
The general research question and its general scientific
and social perspective were proposed by my promotor. I delineated the research
question, described how it fits in the current scientific literature and described its
potential social impact. I revised the text two times, after comments of my co-promotor.

\paragraph{Chapter 2} \dots

\paragraph{Chapter 3 Heat resistance of ice-cream.} 
I contributed to defining the research question,
proposed the methodology and the experimental design, carried out the experiments
together with an MSc student whom I supervised, and did the data analysis together with
the student and a statistician. The student wrote the first draft (therefore, I am second
author) and revised it after the comments of myself (which were quite many) and the
other co-authors.

\paragraph{Chapter 4} \dots

\paragraph{Chapter 5} \dots

\paragraph{Chapter 6 General discussion.}
I wrote the first draft of the text after just one discussion
with my co-promotor on the subjects and arguments to be included. I revised the text
once, after comments of my promotor and co-promotor.

\vspace*{\fill}

{\renewcommand{\arraystretch}{2}
\begin{tabular}{@{}ll@{}}
    Date: & \today{} \\
    Signature PhD candidate: & \\
    Signature promotor for agreement: & 
\end{tabular}
}

\end{document}